PAQ for parenting observational study

### 2017-03-08 paq/parenting_obs_paq.Rmd
added parent_ed analysis

  attitudes_id <- data.frame(workerid = f, 
                   sent = jd$data$sentence[2:25],
                   rating = jd$data$rating[1:24])

@@

@@

paq <- paq %>%
  gather(ques, rating, Q1:Q24)%>%
  mutate(workerid = Sub_ID)%>%
  left_join(sents)%>%
  select(workerid, sent, rating)

@@

@@

atts <- dq %>%
  group_by(workerid, category) %>% 
  summarise(rating = mean(rating))
```

@@

ggplot(atts_m, aes(x = category, y = mean)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))
```

>>>>

  attitudes_id <- data.frame(sid = f, 
                   sent = jd$data$sentence[2:25],
                   rating = jd$data$rating[1:24])

@@

attitudes$sid <- str_replace(attitudes$sid, "parenting_proj_", "")
attitudes$sid <- str_replace(attitudes$sid, ".json", "")

@@

paq <- paq %>%
  gather(ques, rating, Q1:Q24)%>%
  mutate(sid = Sub_ID)%>%
  left_join(sents)%>%
  select(sid, sent, rating)

@@

Read in demographics.

```{r}
demo <- read.csv("../parenting_proj_emilyhembacher_demo2016.csv")

demo <- demo %>%
  mutate(sid = SID)%>%
  select(sid, ethnicity, parent_ed)

attitudes <- left_join(attitudes, demo)
```

@@

atts <- dq %>%
  group_by(sid, category) %>% 
  summarise(rating = mean(rating))
```

@@

ggplot(atts_m, aes(x = category, y = mean)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))
```
```{r}
dq$parent_ed <- as.factor(dq$parent_ed)

mss <- dq %>%
  group_by(sid, parent_ed) %>%
  filter(!is.na(parent_ed))%>%
  multi_boot_standard(col = "rating", na.rm = TRUE)

qplot(parent_ed, data=mss)

ms <- dq %>%
  group_by(parent_ed, category) %>%
  filter(!is.na(parent_ed))%>%
  multi_boot_standard(col = "rating", na.rm = TRUE)

ggplot(ms, aes(category, mean, fill=parent_ed)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```
